---
title: "Math 42 Final"
author: "Barry Qi"
date: "5/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Hair Dryer

```{r}
# Loading Data
hair_dryer <- read.csv("hair_dryer.csv")
hair_dryer_verif <- read.csv("hair_dryer_verif.csv")
hair_dryer_vine <- read.csv("hair_dryer_vine.csv")
```

## Rating versus Number of Reviews

### Collecting the necessary data
```{r}
hair_total_rate <- tapply(hair_dryer[, "star_rating"], hair_dryer[, "product_title"], mean)
hair_total_freq <- tapply(hair_dryer[, "star_rating"], hair_dryer[, "product_title"], length)

hair_verif_rate <- tapply(hair_dryer_verif[, "star_rating"], hair_dryer_verif[, "product_title"], mean)
hair_verif_freq <- tapply(hair_dryer_verif[, "star_rating"], hair_dryer_verif[, "product_title"], length)

hair_vine_rate <- tapply(hair_dryer_vine[, "star_rating"], hair_dryer_vine[, "product_title"], mean)
hair_vine_freq <- tapply(hair_dryer_vine[, "star_rating"], hair_dryer_vine[, "product_title"], length)
```

### Plots of Ratings versus Number of Reviews

```{r}
plot(hair_total_rate, hair_total_freq,
     main = "Ratings versus Number of Reviews for All Reviews (Hair Dryer)",
     xlab = "Rating",
     ylab = "Number of Reviews")
```

```{r}
plot(hair_verif_rate, hair_verif_freq,
     main = "Ratings versus Number of Reviews for Verified Reviews",
     xlab = "Rating",
     ylab = "Number of Reviews")
```

```{r}
plot(hair_vine_rate, hair_vine_freq,
     main = "Ratings versus Number of Reviews for Vine Reviews",
     xlab = "Rating",
     ylab = "Number of Reviews",
     xlim = c(1, 5))
```

### Calculating R-Squared Values

```{r}
hair_total_rsq <- cor(hair_total_rate, hair_total_freq) ^ 2
hair_verif_rsq <- cor(hair_verif_rate, hair_verif_freq) ^ 2
hair_vine_rsq <- cor(hair_vine_rate, hair_vine_freq) ^ 2

hair_total_rsq
hair_verif_rsq
hair_vine_rsq
```
R-squared values are all relatively low and indicate very little correlation.

OVERALL:
Only noticeable trend: All products with low ratings also have a low number of reviews. This may indicate that the first reviews are particularly impactful - if a product has low and few reviews, it may be that people do not purchase the item, therefore keeping the number of reviews low.

### Star Rating versus Helpful Votes
```{r}
plot(hair_dryer[, "star_rating"], hair_dryer[, "helpful_votes"],
     xlab = "Rating",
     ylab = "Number of Helpful Votes",
     main = "Rating versus Number of Helpful Votes")
```

```{r}
hair_rating_help_rsq <- cor(hair_dryer[, "star_rating"], hair_dryer[, "helpful_votes"]) ^ 2
hair_rating_help_rsq
```
No clear relationship between average rating and the number of helpful votes.

## Star Rating versus Verified Purchaser

```{r}
hair_verif <- tapply(hair_dryer[, "star_rating"], hair_dryer[, "verified_purchase"], mean)
barplot(hair_verif,
        col = c("darkred", "darkgreen"),
        xlab = "Verified Purchaser",
        ylab = "Average Rating",
        ylim = c(0, 5),
        main = "Average Rating by Verified Purchaser (Hair Dryer)")
```

```{r}
hair_y_verif_indices <- which(hair_dryer[, "verified_purchase"] == "Y")
hair_n_verif_indices <- which(hair_dryer[, "verified_purchase"] == "N")
t.test(hair_dryer[, "star_rating"][hair_y_verif_indices], hair_dryer[, "star_rating"][hair_n_verif_indices])
```
There is a statistically significant difference that verified purchaser reviewers tend to give higher reviews.

# Star Rating versus Vine

```{r}
hair_vine <- tapply(hair_dryer[, "star_rating"], hair_dryer[, "vine"], mean)
barplot(hair_vine,
        col = c("darkred", "darkgreen"),
        xlab = "Vine Purchaser",
        ylab = "Average Rating",
        ylim = c(0, 5),
        main = "Average Rating by Vine Purchaser Status (Hair Dryer)")
```

```{r}
hair_y_vine_indices <- which(hair_dryer[, "vine"] == "Y")
hair_n_vine_indices <- which(hair_dryer[, "vine"] == "N")
t.test(hair_dryer[, "star_rating"][hair_y_vine_indices], hair_dryer[, "star_rating"][hair_n_vine_indices])
```
There is a statistically significant difference that Vine reviewers tend to give higher reviews.

# Microwave

```{r}
# Loading Data
micro <- read.csv("microwave.csv")
micro_verif <- read.csv("microwave_verif.csv")
micro_vine <- read.csv("microwave_vine.csv")
```

```{r}
micro[, "verified_purchase"][which(micro[, "verified_purchase"] == "n")] <- "N"
micro[, "verified_purchase"][which(micro[, "verified_purchase"] == "y")] <- "Y"

micro[, "vine"][which(micro[, "vine"] == "n")] <- "N"
micro[, "vine"][which(micro[, "vine"] == "y")] <- "Y"
```

## Rating versus Number of Reviews

### Collecting the necessary data
```{r}
micro_total_rate <- tapply(micro[, "star_rating"], micro[, "product_title"], mean)
micro_total_freq <- tapply(micro[, "star_rating"], micro[, "product_title"], length)

micro_verif_rate <- tapply(micro_verif[, "star_rating"], micro_verif[, "product_title"], mean)
micro_verif_freq <- tapply(micro_verif[, "star_rating"], micro_verif[, "product_title"], length)

micro_vine_rate <- tapply(micro_vine[, "star_rating"], micro_vine[, "product_title"], mean)
micro_vine_freq <- tapply(micro_vine[, "star_rating"], micro_vine[, "product_title"], length)
```

### Plots of Ratings versus Number of Reviews

```{r}
plot(micro_total_rate, micro_total_freq,
     main = "Ratings versus Number of Reviews for All Reviews (Microwave)",
     xlab = "Rating",
     ylab = "Number of Reviews")
```

```{r}
plot(micro_verif_rate, micro_verif_freq,
     main = "Ratings versus Number of Reviews for Verified Reviews",
     xlab = "Rating",
     ylab = "Number of Reviews")
```

```{r}
plot(micro_vine_rate, micro_vine_freq,
     main = "Ratings versus Number of Reviews for Vine Reviews",
     xlab = "Rating",
     ylab = "Number of Reviews",
     xlim = c(1, 5))
```

### Calculating R-Squared Values

```{r}
micro_total_rsq <- cor(micro_total_rate, micro_total_freq) ^ 2
micro_verif_rsq <- cor(micro_verif_rate, micro_verif_freq) ^ 2
micro_vine_rsq <- cor(micro_vine_rate, micro_vine_freq) ^ 2

micro_total_rsq
micro_verif_rsq
micro_vine_rsq
```

### Star Rating versus Helpful Votes
```{r}
plot(micro[, "star_rating"], micro[, "helpful_votes"],
     xlab = "Rating",
     ylab = "Number of Helpful Votes",
     main = "Rating versus Number of Helpful Votes")
```

```{r}
micro_rating_help_rsq <- cor(micro[, "star_rating"], micro[, "helpful_votes"]) ^ 2
micro_rating_help_rsq
```

## Star Rating versus Verified Purchaser

```{r}
micro_verif <- tapply(micro[, "star_rating"], micro[, "verified_purchase"], mean)

ratings <- integer(0)
for (i in 1:length(micro[, "verified_purchase"])) {
    if (micro[, "verified_purchase"][i] == "N") {
      ratings[length(ratings) + 1] <- micro[, "star_rating"][i]
    }
  micro_verif[2] <- mean(ratings, na.rm = TRUE)
}

barplot(height = c(micro_verif[2], micro_verif[4]),
        col = c("darkred", "darkgreen"),
        xlab = "Verified Purchaser",
        ylab = "Average Rating",
        ylim = c(0, 5),
        main = "Average Rating by Verified Purchaser (Microwaves)")
```

```{r}
micro_y_verif_indices <- which(micro[, "verified_purchase"] == "Y")
micro_n_verif_indices <- which(micro[, "verified_purchase"] == "N")
t.test(micro[, "star_rating"][micro_y_verif_indices], micro[, "star_rating"][micro_n_verif_indices])
```

# Star Rating versus Vine

```{r}
micro_vine <- tapply(micro[, "star_rating"], micro[, "vine"], mean)

barplot(height = c(micro_vine[2], micro_vine[3]),
        col = c("darkred", "darkgreen"),
        xlab = "Vine Purchaser",
        ylab = "Average Rating",
        ylim = c(0, 5),
        main = "Average Rating by Vine Purchaser Status (Microwave)")
```

```{r}
micro_y_vine_indices <- which(micro[, "vine", ] == "Y")
micro_n_vine_indices <- which(micro[, "vine", ] == "N")
t.test(micro[, "star_rating"][micro_y_vine_indices], micro[, "star_rating"][micro_n_vine_indices])
```

# Pacifier

```{r}
# Loading Data
pacifier <- read.csv("pacifier.csv")
pacifier_verif <- read.csv("pacifier_verif.csv")
pacifier_vine <- read.csv("pacifier_vine.csv")
```

```{r}
pacifier[, "verified_purchase"][which(pacifier[, "verified_purchase"] == "n")] <- "N"
pacifier[, "verified_purchase"][which(pacifier[, "verified_purchase"] == "y")] <- "Y"

pacifier[, "vine"][which(pacifier[, "vine"] == "n")] <- "N"
pacifier[, "vine"][which(pacifier[, "vine"] == "y")] <- "Y"
```

## Rating versus Number of Reviews

### Collecting the necessary data
```{r}
pacifier_total_rate <- tapply(pacifier[, "star_rating"], pacifier[, "product_title"], mean)
pacifier_total_freq <- tapply(pacifier[, "star_rating"], pacifier[, "product_title"], length)

pacifier_verif_rate <- tapply(pacifier_verif[, "star_rating"], pacifier_verif[, "product_title"], mean)
pacifier_verif_freq <- tapply(pacifier_verif[, "star_rating"], pacifier_verif[, "product_title"], length)

pacifier_vine_rate <- tapply(pacifier_vine[, "star_rating"], pacifier_vine[, "product_title"], mean)
pacifier_vine_freq <- tapply(pacifier_vine[, "star_rating"], pacifier_vine[, "product_title"], length)
```

### Plots of Ratings versus Number of Reviews

```{r}
plot(pacifier_total_rate, pacifier_total_freq,
     main = "Ratings versus Number of Reviews for All Reviews (Pacifier)",
     xlab = "Rating",
     ylab = "Number of Reviews")
```

```{r}
plot(pacifier_verif_rate, pacifier_verif_freq,
     main = "Ratings versus Number of Reviews for Verified Reviews",
     xlab = "Rating",
     ylab = "Number of Reviews")
```

```{r}
plot(pacifier_vine_rate, pacifier_vine_freq,
     main = "Ratings versus Number of Reviews for Vine Reviews",
     xlab = "Rating",
     ylab = "Number of Reviews")
```

### Calculating R-Squared Values

```{r}
pacifier_total_rsq <- cor(pacifier_total_rate, pacifier_total_freq) ^ 2
pacifier_verif_rsq <- cor(pacifier_verif_rate, pacifier_verif_freq) ^ 2
pacifier_vine_rsq <- cor(pacifier_vine_rate, pacifier_vine_freq) ^ 2

pacifier_total_rsq
pacifier_verif_rsq
pacifier_vine_rsq
```

### Star Rating versus Helpful Votes
```{r}
plot(pacifier[, "star_rating"], pacifier[, "helpful_votes"],
     xlab = "Rating",
     ylab = "Number of Helpful Votes",
     main = "Rating versus Number of Helpful Votes")
```

```{r}
pacifier_rating_help_rsq <- cor(pacifier[, "star_rating"], pacifier[, "helpful_votes"]) ^ 2
pacifier_rating_help_rsq
```

## Star Rating versus Verified Purchaser

```{r}
pacifier_verif <- tapply(pacifier[, "star_rating"], pacifier[, "verified_purchase"], mean)

ratings <- integer(0)
for (i in 1:length(pacifier[, "verified_purchase"])) {
    if (pacifier[, "verified_purchase"][i] == "N") {
      ratings[length(ratings) + 1] <- pacifier[, "star_rating"][i]
    }
  pacifier_verif[2] <- mean(ratings, na.rm = TRUE)
}

barplot(height = c(pacifier_verif[2], pacifier_verif[4]),
        col = c("darkred", "darkgreen"),
        xlab = "Verified Purchaser",
        ylab = "Average Rating",
        ylim = c(0, 5),
        main = "Average Rating by Verified Purchaser (Pacifier)")
```

```{r}
pacifier_y_verif_indices <- which(pacifier[, "verified_purchase"] == "Y")
pacifier_n_verif_indices <- which(pacifier[, "verified_purchase"] == "N")
t.test(pacifier[, "star_rating"][pacifier_y_verif_indices], pacifier[, "star_rating"][pacifier_n_verif_indices])
```

# Star Rating versus Vine

```{r}
pacifier_vine <- tapply(pacifier[, "star_rating"], pacifier[, "vine"], mean)

barplot(height = c(pacifier_vine[2], pacifier_vine[4]),
        col = c("darkred", "darkgreen"),
        xlab = "Vine Purchaser",
        ylab = "Average Rating",
        ylim = c(0, 5),
        main = "Average Rating by Vine Purchaser Status (Pacifier)")
```

```{r}
pacifier_y_vine_indices <- which(pacifier[, "vine"] == "Y")
pacifier_n_vine_indices <- which(pacifier[, "vine"] == "N")
t.test(pacifier[, "star_rating"][pacifier_y_vine_indices], pacifier[, "star_rating"][pacifier_n_vine_indices])
```
