---
title: "FinalProject-TextMining"
output: pdf_document
---
```{r,message=FALSE}
library(tidytext)
library(tidyverse)
```

# 1) Load in Data
```{r,message=FALSE}
dryer <- read_csv("hair_dryer_verif.csv") # only interested in verified purchases
paci <- read_csv("pacifier_verif.csv")
micro <- read_csv("microwave_verif.csv")
head(dryer)
head(paci)
head(micro)
```



# 2) Data Preparation
Separate review headline, body, and product title into individual words to look for correlation between words and other factors

Define Stopwords
```{r}
stop_words_es <- stopwords::stopwords("es", source = "stopwords-iso")
stop_words_fr <- stopwords::stopwords("fr", source = "stopwords-iso")
stop_words_en <- stopwords::stopwords("en", source = "stopwords-iso")
stop_words_extra <- c("i’m","we’re","it’s","you’re","that’s","they’ve")
stop_words_
stop_words_comp <- c(stop_words_es,stop_words_fr,stop_words_en,stop_words_extra)
stop_words_comp <- data.frame("word" = stop_words_comp, lexicon = 'SMART',stringsAsFactors = F)
```

function to unnest into indiv words 
```{r}
# df: dataframe that contains words
# words: words to unnest
# additional: additional columns to select
words_unnest <- function(df,words,additional){
  unnested <- df %>% unnest_tokens(word,!!words) %>% anti_join(stop_words_comp) %>% select(!!additional)
  return(unnested)
}
```

Create base word dataframes to perform analysis on
```{r,message=F}
# unnest captions into individual words
dryer_head <- words_unnest(dryer,quo(review_headline),quo(c(review_id,review_date,word,star_rating,helpful,vine)))
dryer_body <- words_unnest(dryer,quo(review_body),quo(c(review_id,review_date,word,star_rating,helpful,vine)))
dryer_p_title <- words_unnest(dryer,quo(product_title),quo(c(review_id,review_date,word,star_rating,helpful,vine)))
# head(dryer_p_title)

micro_head <- words_unnest(micro,quo(review_headline),quo(c(review_id,review_date,word,star_rating,helpful,vine)))
micro_body <- words_unnest(micro,quo(review_body),quo(c(review_id,review_date,word,star_rating,helpful,vine)))
micro_p_title <- words_unnest(micro,quo(product_title),quo(c(review_id,review_date,word,star_rating,helpful,vine)))

paci_head <- words_unnest(paci,quo(review_headline),quo(c(review_id,review_date,word,star_rating,helpful,vine)))
paci_body <- words_unnest(paci,quo(review_body),quo(c(review_id,review_date,word,star_rating,helpful,vine)))
paci_p_title <- words_unnest(paci,quo(product_title),quo(c(review_id,review_date,word,star_rating,helpful,vine)))
```

function to count words and find avg star rating per word
```{r}
# df: dataframe that contains words
words_count_rtg <- function(df){
  word_ct_rtg <- df %>% select(-c(review_id,review_date)) %>% 
  group_by(word) %>% mutate(word_count=n(),avg_star = mean(star_rating)) %>% # find word count + avg star rating for each word 
  arrange(desc(word_count)) %>% select(-star_rating)
  
  word_ct_rtg <- word_ct_rtg[!(duplicated(word_ct_rtg$word)),] # remove duplicates of each word
  return(word_ct_rtg)
}
```

Find these values for header, body, and product title
```{r}
dryer_head_ct <- words_count_rtg(dryer_head)
dryer_body_ct <- words_count_rtg(dryer_body)
dryer_p_title_ct <- words_count_rtg(dryer_p_title)
```

Define frequent words as having counts > 5 appearances for review headers and product titles and > 200 appearances for review bodies (since we at least want to retain 1 quartile of data)
```{r}
dryer_head_ct <- dryer_head_ct %>% filter(word_count > 10) %>% arrange(desc(avg_star))
dryer_body_ct <- dryer_body_ct %>% filter(word_count > 200) %>% arrange(desc(avg_star))
dryer_p_title_ct <- dryer_p_title_ct %>% filter(word_count > 10) %>% arrange(desc(word_count))
dryer_head_ct$word <- factor(dryer_head_ct$word, levels = dryer_head_ct$word) # keeps order for barplot
dryer_body_ct$word <- factor(dryer_body_ct$word, levels = dryer_body_ct$word)
dryer_p_title_ct$word <- factor(dryer_p_title_ct$word, levels = dryer_p_title_ct$word)
head(dryer_body_ct)
```

Repeat for Microwave
```{r}
micro_head_ct <- words_count_rtg(micro_head)
micro_body_ct <- words_count_rtg(micro_body)
micro_p_title_ct <- words_count_rtg(micro_p_title)
```

Not as many microwave reviews so lower cutoff for filter
```{r}
micro_head_ct <- micro_head_ct %>% filter(word_count > 2) %>% arrange(desc(avg_star))
micro_body_ct <- micro_body_ct %>% filter(word_count > 5) %>% arrange(desc(avg_star))
micro_p_title_ct <- micro_p_title_ct %>% filter(word_count > 2) %>% arrange(desc(word_count))
micro_head_ct$word <- factor(micro_head_ct$word, levels = micro_head_ct$word) # keeps order for barplot
micro_body_ct$word <- factor(micro_body_ct$word, levels = micro_body_ct$word)
micro_p_title_ct$word <- factor(micro_p_title_ct$word, levels = micro_p_title_ct$word)
```

Repeat for Pacifier
```{r}
paci_head_ct <- words_count_rtg(paci_head)
paci_body_ct <- words_count_rtg(paci_body)
paci_p_title_ct <- words_count_rtg(paci_p_title)
```

Lots of pacifier reviews so higher cutoff for filter
```{r}
paci_head_ct <- paci_head_ct %>% filter(word_count > 20) %>% arrange(desc(avg_star))
paci_body_ct <- paci_body_ct %>% filter(word_count > 200) %>% arrange(desc(avg_star))
paci_p_title_ct <- paci_p_title_ct %>% filter(word_count > 50) %>% arrange(desc(word_count))
paci_head_ct$word <- factor(paci_head_ct$word, levels = paci_head_ct$word) # keeps order for barplot
paci_body_ct$word <- factor(paci_body_ct$word, levels = paci_body_ct$word)
paci_p_title_ct$word <- factor(paci_p_title_ct$word, levels = paci_p_title_ct$word)
```


# 3) Graphs
Define custom color sets
```{r}
cbp <- c("#999999", "#E69F00", "#56B4E9", "#009E73",
          "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
show_col(cbp)
```

Still need to filter out words it seems...
```{r}
dh <- ggplot(head(dryer_head_ct,20),aes(x=reorder(word,avg_star),y=avg_star,fill=avg_star)) + geom_bar(stat="identity") + 
  theme_minimal() + theme(text = element_text(size=15)) + scale_fill_gradient() + coord_flip() + 
  ggtitle("Review Heading Highest Rated Words") + ylab("Average Star Rating") + xlab("Word")
dh
```

Lots of words not related to features: wow, terrific, highly, wonderful, excellent, filter these out
also in title, filter out nondescriptive words/pronouns -> make function
```{r}
remove_nonsense <- function(df,nonsense){
  df <- df[!df$word %in% nonsense,]
  return(df)
}
```

```{r}
nonsense <- c("wow","terrific","highly","awesome","finally","love","wonderful",
              "excellent","loves","amazing","lots","perfect","fabulous","favorite",
              "christmas","fantastic","super","glad","solid","satisfied","absolutely",
              "stars","happy","nice","recommend",
              "dissapointed","dissapointing","poor","horrible","star","amazon",
              "reviews","meh")
pronouns <- c("dryer","hair","conair","1875","andis","1875w","revlon","remington","1600","ac2015")
```

Refilter
```{r}
dryer_head_ct2 <- remove_nonsense(dryer_head_ct,nonsense)
dryer_body_ct2 <- remove_nonsense(dryer_body_ct,nonsense)
dryer_p_title_ct2 <- remove_nonsense(dryer_p_title_ct,nonsense)
```

Try plotting again
```{r}
dh2 <- ggplot(head(dryer_head_ct2,20),aes(x=reorder(word,avg_star),y=avg_star,fill=avg_star)) + geom_bar(stat="identity") + 
  theme_minimal() + theme(text = element_text(size=15)) + scale_fill_gradient() + coord_flip() + 
  ggtitle("Review Heading Highest Rated Words") + ylab("Average Star Rating") + xlab("Word")

db2 <- ggplot(head(dryer_body_ct2,20),aes(x=reorder(word,avg_star),y=avg_star,fill=avg_star)) + geom_bar(stat="identity") + 
  theme_minimal() + theme(text = element_text(size=15)) + scale_fill_gradient() + coord_flip() + 
  ggtitle("Review Body Highest Rated Words") + ylab("Average Star Rating") + xlab("Word")

dpt2 <- ggplot(head(dryer_p_title_ct2,20),aes(x=reorder(word,word_count),y=word_count,fill=word_count)) + 
  geom_bar(stat="identity") + 
  theme_minimal() + theme(text = element_text(size=15)) + scale_fill_gradient() + coord_flip() + 
  ggtitle("Product Title Most Frequent Words")+ ylab("Average Star Rating") + xlab("Word")
dh2; db2; dpt2
```

Look at lowest rated words
```{r}
dh3 <- ggplot(tail(dryer_head_ct2,20),aes(x=reorder(word,avg_star),y=avg_star,fill=avg_star)) + geom_bar(stat="identity") + 
  theme_minimal() + theme(text = element_text(size=15)) + scale_fill_gradient(low = "#431913",high = "#f76b56") + coord_flip() + 
  ggtitle("Review Heading Lowest Rated Words") + ylab("Average Star Rating") + xlab("Word")

db3 <- ggplot(tail(dryer_body_ct2,20),aes(x=reorder(word,avg_star),y=avg_star,fill=avg_star)) + geom_bar(stat="identity") + 
  theme_minimal() + theme(text = element_text(size=15)) + scale_fill_gradient(low = "#431913",high = "#f76b56") + coord_flip() + 
  ggtitle("Review Body Lowest Rated Words") + ylab("Average Star Rating") + xlab("Word")
dh3; db3
```

Repeat for Microwaves
```{r}
# add more nonsense words
nonsense <- c(nonsense,"expected","700","perfectly","limited","pleased","complaints","microwave","fine","issues",
              "disappointed","recommended")
pronouns <- c(pronouns,"microwave","microwaves","countertop","danby","oven","range","98qbp0302","kit","samsung",
              "wmc20005yd","om75p","wb27x10017","wmc20005yw","mc11h6033ct","whirlpool","lg")
```

```{r}
micro_head_ct2 <- remove_nonsense(micro_head_ct,nonsense)
micro_body_ct2 <- remove_nonsense(micro_body_ct,nonsense)
micro_p_title_ct2 <- remove_nonsense(micro_p_title_ct,pronouns)
```

```{r}
mh2 <- ggplot(head(micro_head_ct2,20),aes(x=reorder(word,avg_star),y=avg_star,fill=avg_star)) + geom_bar(stat="identity") + 
  theme_minimal() + theme(text = element_text(size=15)) + scale_fill_gradient() + coord_flip() + 
  ggtitle("Review Heading Highest Rated Words") + ylab("Average Star Rating") + xlab("Word")

mb2 <- ggplot(head(micro_body_ct2,20),aes(x=reorder(word,avg_star),y=avg_star,fill=avg_star)) + geom_bar(stat="identity") + 
  theme_minimal() + theme(text = element_text(size=15)) + scale_fill_gradient() + coord_flip() + 
  ggtitle("Review Body Highest Rated Words") + ylab("Average Star Rating") + xlab("Word")

mpt2 <- ggplot(head(micro_p_title_ct2,20),aes(x=reorder(word,word_count),y=word_count,fill=word_count)) + 
  geom_bar(stat="identity") + 
  theme_minimal() + theme(text = element_text(size=15)) + scale_fill_gradient() + coord_flip() + 
  ggtitle("Product Title Most Frequent Words")+ ylab("Average Star Rating") + xlab("Word")
mh2; mb2; mpt2
```
```{r}
mh3 <- ggplot(tail(micro_head_ct2,10),aes(x=reorder(word,avg_star),y=avg_star,fill=avg_star)) + geom_bar(stat="identity") + 
  theme_minimal() + theme(text = element_text(size=15)) + scale_fill_gradient(low = "#431913",high = "#f76b56") + coord_flip() + 
  ggtitle("Review Heading Lowest Rated Words") + ylab("Average Star Rating") + xlab("Word")

mb3 <- ggplot(tail(micro_body_ct2,20),aes(x=reorder(word,avg_star),y=avg_star,fill=avg_star)) + geom_bar(stat="identity") + 
  theme_minimal() + theme(text = element_text(size=15)) + scale_fill_gradient(low = "#431913",high = "#f76b56") + coord_flip() + 
  ggtitle("Review Body Lowest Rated Words") + ylab("Average Star Rating") + xlab("Word")
mh3; mb3
```

Repeat for Pacifiers
```{r}
pronouns <- c(pronouns,"pacifier","pacifiers")
```


```{r}
paci_head_ct2 <- remove_nonsense(paci_head_ct,nonsense)
paci_body_ct2 <- remove_nonsense(paci_body_ct,nonsense)
paci_p_title_ct2 <- remove_nonsense(paci_p_title_ct,pronouns)
```

```{r}
ph2 <- ggplot(head(paci_head_ct2,20),aes(x=reorder(word,avg_star),y=avg_star,fill=avg_star)) + geom_bar(stat="identity") + 
  theme_minimal() + theme(text = element_text(size=15)) + scale_fill_gradient() + coord_flip() + 
  ggtitle("Review Heading Highest Rated Words") + ylab("Average Star Rating") + xlab("Word")

pb2 <- ggplot(head(paci_body_ct2,20),aes(x=reorder(word,avg_star),y=avg_star,fill=avg_star)) + geom_bar(stat="identity") + 
  theme_minimal() + theme(text = element_text(size=15)) + scale_fill_gradient() + coord_flip() + 
  ggtitle("Review Body Highest Rated Words") + ylab("Average Star Rating") + xlab("Word")

ppt2 <- ggplot(head(paci_p_title_ct2,20),aes(x=reorder(word,word_count),y=word_count,fill=word_count)) + 
  geom_bar(stat="identity") + 
  theme_minimal() + theme(text = element_text(size=15)) + scale_fill_gradient() + coord_flip() + 
  ggtitle("Product Title Most Frequent Words")+ ylab("Average Star Rating") + xlab("Word")
ph2; pb2; ppt2
```

```{r}
ph3 <- ggplot(tail(paci_head_ct2,20),aes(x=reorder(word,avg_star),y=avg_star,fill=avg_star)) + geom_bar(stat="identity") + 
  theme_minimal() + theme(text = element_text(size=15)) + scale_fill_gradient(low = "#431913",high = "#f76b56") + coord_flip() + 
  ggtitle("Review Heading Lowest Rated Words") + ylab("Average Star Rating") + xlab("Word")

pb3 <- ggplot(tail(paci_body_ct2,20),aes(x=reorder(word,avg_star),y=avg_star,fill=avg_star)) + geom_bar(stat="identity") + 
  theme_minimal() + theme(text = element_text(size=15)) + scale_fill_gradient(low = "#431913",high = "#f76b56") + coord_flip() + 
  ggtitle("Review Body Lowest Rated Words") + ylab("Average Star Rating") + xlab("Word")
ph3; pb3
```



